D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-08 ootavacuous.tex
Remove prototype wording section
Perhaps revert this commit at a later time?

Reported-by: Maged Michael <maged.michael@gmail.com>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\section{Suggested Changes to Wording}
\label{sec:Suggested Changes to Wording}

Add the following note in \co{[atomics.order]} after 33.5.4p9:

\begin{quote}
	[ \emph{Note:} Implementations that respect the following
	constraints are incapable of computing out-of-thin-air value
	that depend circularly on their own computation:

	\begin{itemize}
	\item	Correctly implement the C++ abstract machine, and
	\item	Run on correctly implemented hardware
		(specifically, hardware that forbids non-speculative
		loads from returning values from speculative stores
		and that forbids exposing values from speculative
		stores to other threads), and
	\item	Reside in a universe having a finite speed of light
		and atomic matter.
	\end{itemize}

	All three constraints are subject to the as-if rule.
	For example, those creating an alternate universe in which
	C++ implementations are to run correctly should ensure
	that their universe behaves as if the speed of light was
	finite and the nature of matter was atomic.
	--- \emph{end note} ]
\end{quote}

@@

% @@@ TODO:
% Update wording.
% Add more detail on blocking UB to "Aside on Undefined Behavior".

>>>>

@@

% @@@ TODO:
% Add more detail on blocking UB to "Aside on Undefined Behavior".
